Qubit Storage in a Decoherence-Free Subspace with Nitrogen-Vacancy Centers and $^{13}$C Nuclear Spins

### 2016-07-20 swap-nvst-paper/paper.tex
slight reorganization of paper

@@

\section{Addressing symmetric $^{13}$C nuclear spins}

@@

@@

>>>>

\fixme{Write about NV centers, C-13 nuclei, introduction to larmor
  pairs and DFS, quantum memory/networks, etc.}

@@

\section{Identifying symmetrically coupled $^{13}$C nuclear spins}

\fixme{How do we identify and locate larmor pairs?}

\section{Individually addressing larmor pairs}

\fixme{How do we individually address larmor pairs?}

@@

\fixme{Implement PRX\cite{reiserer2016robust} methods for initializing
  a qubit in $\ket{\u\d}\pm\ket{\d\u}$}

@@

\section{Coherent SWAP operation with DFS qubit}
